\documentclass{resume}

\usepackage[left=0.75in,top=0.6in,right=0.75in,bottom=0.6in]{geometry}

\name{Joseph Cherian Kariampally}
\address{ Flat 603, Azizi Feirouz, Al Furjan \\ Jabel Ali, Dubai  }
\address{ +971~$\cdot$~567296980 \\ joseph.kariampally@gmail.com \\ https://github.com/JCherry101 \\ www.linkedin.com/in/joseph-cherian-a37813169}

\def\nameskip{\bigskip}
\def\sectionskip{\medskip}

\begin{document}

  \begin{rSection}{Education}
    {\bf Heriot Watt University, Dubai} \hfill {\em September 2023 - Ongoing (Expected May 2026)} \\ 
    { BSc in Computer Science \& Hons in Data Science} \smallskip \\
    Current GPA: 3.74 (On Conversion to US GPA scale 4.0)
  \end{rSection}
  
  \begin{rSection}{Projects, Experience, and other work}{https://github.com/JCherry101}
  
    \begin{rSubsection}{Plug Saver (Software Engineering)}{https://plugsaver77.weebly.com/}{Backend and Database Management}{Heriot Watt University}
    \item Worked with my team during my third year in university to develop a Web application that simulates the the functionality of a real world smart home plug.
    \item Used Python to develop the Back-end functions and Flask to create a REST API to communicate with Front-end.
    \item Created the database using PostgreSQL in Supabase.com for live upkeep of the application and data storage.
    \item Understood the basics to work with a team and implement SCRUM and AGILE methodologies to achieve the final task in the project.
    \end{rSubsection}
  
    \begin{rSubsection}{Hardware-Software Interface}{January 2024 - May 2024}{Developer}{Heriot Watt University}
    \item Developed a MasterMind game on Raspberry Pi 2 using C and ARM Assembly, integrating LEDs, a button, and an LCD for user interaction, with hardware control through GPIO and optimized performance using inline and pure assembly code.
    \item Learnt to use basic hardware and also was introduced to Linux OS indepth and its commands.
    \end{rSubsection}

    \begin{rSubsection}{RedTeam CyberHack CTF Competition}{19th January, 2025}{CTF Competition}{Dubai, UAE}
    \item Won the first place at the Cyber Hack: Capture The Flag (CTF) event hosted by the Heriot Watt Tech Club in Partnership with the REDTEAM Hacker Academy.
    \item Learnt to navigate the quick and challenging pace of competitions and learnt a lot in how cybersecurity challenges are handled in the real world.
    \end{rSubsection}

    \begin{rSubsection}{Udemy Courses}{April 2024 - August 2024}{Certificate Courses}{Dubai, UAE}
    \item Successfully completed 3 certificate courses on Udemy.com
    \item The Data Science Course: Complete Data Science Bootcamp 2025 taught by 365 Careers on Udemy.
    \item Machine Learning A-Z: AI, Python & R taught by Kirill Eremenko, Hadelin de Ponteves, SuperDataScience Team, Ligency Team.
    \item Tableau A-Z: Hands-On Tableau Training for Data Science  taught by Kirill Eremenko, SuperDataScience Team, Ligency Team.
    \end{rSubsection}

    \begin{rSubsection}{Extra and Co-Curricular Activities}
      \item Attended lecture session on Artificial Intelligence by companies Careem, IBM, Microsoft and SAP organized by The United Arab Emirates Minister of State for Artificial Intelligence Office.
      \item Attended a program for development for leadership, social, and presentation skills at Stanford University organized by You Co Lead. Also visited major tech headquarters (Facebook and Apple) and had their campus tours.
      \item Attended lecture session on at the WET EX 2019 Dubai Solar Show organized by Dubai Electricity & Water Authority
      \item Won 1st in a French short film competition (Bataille de Films - Category 2) organized by St.Theresa's College, Ernakulam
      \end{rSubsection}
    
  \end{rSection}
  
  \begin{rSection}{Technical Strengths}
    \begin{tabular}{ @{} >{\bfseries}l @{\hspace{6ex}} l }
      Computer Languages & Python, Java, R, C \\
      Protocols \& APIs & XML, JSON, REST \\
      Databases & MySQL, PostgreSQL \\
      Tools & Tableau, Git, R Studio, Docker \\
    \end{tabular}
  \end{rSection}

\end{document}
